### 2016-06-04 w-wires/paper_gerasimovda.tex
More prettification

\newcommand{\mcL}{\mathcal{L}}
\newcommand{\mcO}{\mathcal{O}}
\newcommand{\mcH}{\mathcal{H}}
\newcommand{\bbT}{\mathbb{T}}
\newcommand{\bbC}{\mathbb{C}}
\newcommand{\bbR}{\mathbb{R}}
\newcommand{\bbD}{\mathbb{D}}

@@

For the computational convenience, $C_r$ is parameterized via $k = R(r) \eexp{\iu t} + \iu C(r)$. After throwing away constants which don't affect the integrals convergence we get the final form of the criterion, which we will use further:

@@

\begin{equation}\label{critp}
\lim\limits_{r \to 1} \int\limits_{0}^{2 \pi} \ln \abs{\det S(R(r) \eexp{\iu t} + \iu C(r))} \frac{R}{(R(r) \eexp{\iu t} + \iu C(r) + i)^2} dt = 0
\end{equation}

@@

Simplifying, we get:

\[
\det S(k) = \frac{W {\left(a + b\right)} k \cos\left(k\right) + 2 i \, W k^{2} \cos\left(k\right) + {\left(i \, a + i \, b\right)} k \sin\left(k\right) - {\left({\left(W^{2} + 1\right)} k^{2} - a b\right)} \sin\left(k\right)}{W {\left(a + b\right)} k \cos\left(k\right) - 2 i \, W k^{2} \cos\left(k\right) - {\left(i \, a + i \, b\right)} k \sin\left(k\right) - {\left({\left(W^{2} + 1\right)} k^{2} - a b\right)} \sin\left(k\right)}
\]

\section{Proof of completeness for $a = b = 0$}
Under the substitituion $a = 0, b = 0$, $\det S$ simplifies to:

\[
\det S(k) = - \frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}
\]

Also, for the sake of brevity, we define

, so we seek the proof of convergence of integral \todo{blah blah $s(k)$}

@@

Suppose we fixed $r$, also for the sake of readability, define $C = C(r)$, $R = R(r)$. For each such $r$, we will estimate the integral and prov that these estimates converge to zero. To do that, we will use the Cauchy-Schwartz inequality:

\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\| \left\|v\right\|
\]

, or, to be more specific, its $\mcL^2[a, b]$ version:

\[
\abs{
\int\limits_{t=a}^{b} f(t) g^*(t) dt
}^2
\le
\int\limits_{t=a}^b \abs{f(t)}^2 dt 
\int\limits_{t=a}^b \abs{g(t)}^2 dt 
\]

To make use of the inequality, we split the integrand of (\ref{critp}) into $f(t) g^*(t)$:
\begin{align*}
a      &= 0 \\
b      &= 2 \pi \\
f(t)   &= \ln s(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g^*(t) &= \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{align*}
Next, we will show that $\int \abs{g(t)}^2$ has an upper bound independent of $r$, and $\int \abs{f(t)}^2$ converges to $0$ as $r$ goes to $1$, which immediately results in convergence to zero for (\ref{critp}).

@@

Since the function \todo{which} is convex on $0 \le y \le Z$, it can be approximated from below with its first derivative at $0$. However, just this will violate the \todo{positiveness??} property, so we have to approximate the function at $Z$ with its first derivative as well, and then glue them together at some point $Z_0$:

@@

First we will compute an upper bound for the integrand. Notice that for $C - R \le y \le \frac{V}{4}$:

\todo{???}
\begin{align*}
    & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}} \\
\le & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\end{align*}

We compute the upper bound for the integrand \todo{$\int\limits_{y = C - R }^{V/4}$ }.

\[
\ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R - C + y}} \frac{1}{\sqrt{R + C - y}}
\]

We use the inequality $\frac{x}{1 + x} \le \ln (1 + x)$ for $x > -1$, where $x = -\frac{2}{V} y$. In this case, since the argument of the logarithm is less than $1$, $(1 + x)^2 \le \frac{x^2}{(1 + x)^2}$.

\[
\le \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V}y)^2} \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R - C + y}} \frac{1}{\sqrt{R + C - y}}
\]

@@

\todo{dammit, finish this}

@@

\[
\frac{\ln \frac{2 (C + 1) C + R^2 - C^2 + 1}{2 (C + 1) (Z + \frac{1}{R}) + R^2 - C^2 + 1}}{2 (C + 1)} = \frac{\mcO(\ln(C^2 + R^2)) + \mcO(TODO)}{C + 1}
\]

@@

Integral of $\frac{1}{\sqrt{R + C - y}}$ from $C$ to $C + R$ is trivial and equals to $2 \sqrt{R}$.

\todo{Simplify, it's clear that integral goes to zero}

>>>>

\newcommand{\mcL}{\mathcal{L}}
\newcommand{\mcO}{\mathcal{O}}
\newcommand{\mcH}{\mathcal{H}}

\newcommand{\bbT}{\mathbb{T}}
\newcommand{\bbC}{\mathbb{C}}
\newcommand{\bbR}{\mathbb{R}}
\newcommand{\bbD}{\mathbb{D}}

@@

For the computational convenience, $C_r$ is parameterized via $C_r = \{R(r) \eexp{\iu t} + \iu C(r) \mid t \in [0, 2 \pi)\}$. For brevity, we define:

, and after throwing away constants which don't affect convergence we get the final form of the criterion, which we will use further:

@@

\begin{equation}\label{critp}
\lim\limits_{r \to 1} \int\limits_{0}^{2 \pi} \ln s(R(r) \eexp{\iu t} + \iu C(r)) \frac{R}{(R(r) \eexp{\iu t} + \iu C(r) + i)^2} dt = 0
\end{equation}

@@

Simplifying, we get:
\[
\det S(k) = \frac{W {\left(a + b\right)} k \cos\left(k\right) + 2 i \, W k^{2} \cos\left(k\right) + {\left(i \, a + i \, b\right)} k \sin\left(k\right) - {\left({\left(W^{2} + 1\right)} k^{2} - a b\right)} \sin\left(k\right)}{W {\left(a + b\right)} k \cos\left(k\right) - 2 i \, W k^{2} \cos\left(k\right) - {\left(i \, a + i \, b\right)} k \sin\left(k\right) - {\left({\left(W^{2} + 1\right)} k^{2} - a b\right)} \sin\left(k\right)}
\]

\section{Proof of completeness for $a = b = 0$}
For simplicity, first we take look at the case $a = 0, b = 0$. After the substitution, we obtain:
\[
s(k) = \abs{\det S(k)} = \abs{\frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}}
\]

@@

Suppose we fixed $r$, also for the sake of readability, define $C = C(r)$, $R = R(r)$. For each such $r$, we will estimate the integral and prov that these estimates converge to zero. To do that, we will use the Cauchy-Schwartz inequality:
\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\| \left\|v\right\|
\]
, or, to be more specific, its $\mcL^2[a, b]$ version:
\[
\abs{
\int\limits_{t=a}^{b} f(t) g^*(t) dt
}^2
\le
\int\limits_{t=a}^b \abs{f(t)}^2 dt 
\int\limits_{t=a}^b \abs{g(t)}^2 dt 
\]
% 
To make use of the inequality, we split the integrand of (\ref{critp}) into $f(t) g^*(t)$:
\begin{align*}
a      &= 0 \\
b      &= 2 \pi \\
f(t)   &= \ln s(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g^*(t) &= \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{align*}
Next, we will show that $\int \abs{g(t)}^2$ has an upper bound independent of $r$, and $\int \abs{f(t)}^2$ converges to $0$ as $r$ goes to $1$, which immediately results in convergence to zero for (\ref{critp}).

@@

Since $l_1$ is convex on $0 \le y \le Z$, it can be approximated from below with its first derivative at $0$. However, just this will violate the property of the estimate being positive (it is under the logarithm sign), so we have to be more careful and approximate the function at $Z$ with its first derivative as well, and then glue them together at some point $Z_0$:

@@

First we will compute an upper bound for the integrand. Notice that for $C - R \le y \le \frac{V}{4}$:
\begin{align*}
       & \ln^2 s(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
\\ \le & \ln^2 s(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\end{align*}

Next, we use the inequality $\frac{x}{1 + x} \le \ln (1 + x)$ for $x > -1$, where $x = -\frac{2}{V} y$. In this case, since the argument of the logarithm is less than $1$, $\ln^2 (1 + x) \le \frac{x^2}{(1 + x)^2}$.

\begin{align*}
       & \dots 
\\ \le & \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V}y)^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\end{align*}

@@

\todo{dammit, finish this. Ugh, we probably can just notice thate $\ln^2 f(y) \frac{1}{\sqrt{R + C - y}}$ grows and then calculate its value?}

@@

\[
\frac{\ln \frac{2 (C + 1) C + R^2 - C^2 + 1}{2 (C + 1) (Z + \frac{1}{R}) + R^2 - C^2 + 1}}{2 (C + 1)} = \frac{\mcO(\ln(C^2 + R^2)) + \mcO(\todo{TODO})}{C + 1}
\]

@@

Integral of $\frac{1}{\sqrt{R + C - y}}$ from $C$ to $C + R$ is trivial and equals to $2 \sqrt{R}$. \todo{Simplify, it's clear that integral goes to zero}
